---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ggwidth

<!-- badges: start -->
<!-- badges: end -->

The objective of ggwidth is to standardise the appearance of the width in ggplot2 geoms.

This works with geoms such as:

* `geom_bar`/`geom_col`
* `geom_boxplot`
* `geom_errorbar`
* `ggbeeswarm::geom_quasirandom`

It ensures that these geoms appear to have visually consistent width across 
plots with different categories, panel dimensions, and orientations.

Note this function:

* requires a set theme with panel widths and heights specified
* requires `"x"` orientation plots to have a x discrete scale with default expand
* requires `"y"` orientation plots to have a y discrete scale with default expand.

## Installation

You can install the development version of ggwidth from [GitHub](https://github.com/) with:

```r
# install.packages("pak")
pak::pak("davidhodge931/ggwidth")
```

```{r setup}
library(ggplot2)
library(dplyr)
library(ggwidth)
library(patchwork)

set_theme(
  theme_grey() +
    theme(panel.widths  = rep(unit(75, "mm"), 2)) +
    theme(panel.heights = rep(unit(50, "mm"), 2))
)

set_equiwidth(1)
```
```{r example-1}
p1 <- palmerpenguins::penguins |>
  filter(!is.na(sex)) |>
  ggplot(aes(x = species)) +
  geom_bar(
    width = get_width(n = 3),
  )

p2 <- diamonds |>
  ggplot(aes(x = color)) +
  geom_bar(width = get_width(n = 7))

p3 <- diamonds |>
  ggplot(aes(y = color)) +
  geom_bar(
    width = get_width(n = 7, orientation = "y"),
  )

p4 <- palmerpenguins::penguins |>
  filter(!is.na(sex)) |>
  ggplot(aes(x = sex, group = species)) +
  geom_bar(
    position = position_dodge(),
    width = get_width(n = 2, dodge_n = 3),
  )

p1 + p2 + p3 + p4
```
```{r example-2}
d <- tibble::tibble(
  continent = c("Europe", "Europe", "Europe", "Europe", "Europe",
                "South America", "South America"),
  country   = c("AT", "DE", "DK", "ES", "PK", "TW", "BR"),
  value     = c(10L, 15L, 20L, 25L, 17L, 13L, 5L)
)

max_n <- d |>
  count(continent) |>
  pull(n) |>
  max()

d |>
  mutate(country = forcats::fct_rev(country)) |>
  ggplot(aes(y = country, x = value)) +
  geom_col(
    width = get_width(n = max_n, orientation = "y"),
  ) +
  facet_wrap(~continent, scales = "free_y") +
  scale_y_discrete(continuous.limits = c(1, max_n)) +
  coord_cartesian(reverse = "y", clip = "off")
```

```{r example-3}
palmerpenguins::penguins |>
  filter(!is.na(sex)) |>
  ggplot(aes(x = species)) +
  geom_bar(
    width = get_width(n = 3, panel_widths = unit(160, "mm")),
  ) +
  theme(panel.widths  = unit(160, "mm"))
```
